Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-18 paper/paper.Rmd
remove `scale_*_continuous()` lines for autoplot() parts

```{r buffer, fig.cap='Visualization of the spatial buffering method from package blockCV (method "spcv\\_buffer" in  mlr3spatiotempcv). The buffer distance is 1000 m.', out.width="40%", fig.pos="ht"}
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

autoplot(resampling_buffer,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

<!-- AB: TODO: folds = 5 makes very little sense in the case of LODO-CV, since this would only sample 5 discs, which cover only a small fraction of the study area. Let's use folds = 100, this will at least make readers think about their choice of #folds. -->
```{r disc, fig.cap='Visualization of one training set / test set combination generated with the leave-one-disc-out method from package sperrorest (method "spcv\\_disc" in mlr3spatiotempcv). The disc has a radius of 300 m and is surrounded by a 400-m buffer.', out.width="40%"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
resampling_disc = rsmp("spcv_disc", folds = 100, radius = 300L, buffer = 400L)
resampling_disc$instantiate(task)

autoplot(resampling_disc,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r coords, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package sperrorest (method "spcv\\_coords" in mlr3spatiotempcv).', out.width="40%", fig.pos="ht"}
resampling_coords = rsmp("spcv_coords", folds = 5)$instantiate(task)

autoplot(resampling_coords,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r tile, fig.cap='Leave-one-block-out resampling from package sperrorest (method "spcv\\_tiles" in package mlr3spatiotempcv with argument nsplit = c(3,4) indicating the number of rows and columns).', out.width="40%", fig.pos="ht"}
resampling_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

autoplot(resampling_tiles,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

<!-- TODO: AB: This diagram is inconsistent with the other diagrams - should display training and test samples. -->
```{r custom-cv, fig.cap='Leave-one-level-out (custom) resampling from package mlr3 (method "custom\\_cv"). A factor variable is used to define the partitions. Each color represents one partition.', out.width="40%", fig.pos="ht"}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

resampling_custom = rsmp("custom_cv")
resampling_custom$instantiate(task, f = zclass)

autoplot(resampling_custom, size = 0.8, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-random, fig.cap='Random resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "random" in mlr3spatiotempcv). The size of the squares is 1000 m, and four out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht"}
resampling_block_random = rsmp("spcv_block", range = 1000, folds = 5)

autoplot(resampling_block_random,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-systematic, fig.cap='Sytematic resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "systematic" in mlr3spatiotempcv). The size of the squares is 1000 m, and four out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht"}
resampling_block_systematic = rsmp("spcv_block",
  range = 1000, folds = 5,
  selection = "systematic"
)

autoplot(resampling_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-checkerboard, fig.cap='Checkerboard resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "checkerboard" in mlr3spatiotempcv). The size of the squares is 1000 m, and eleven out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht!"}
resampling_block_checkerboard = rsmp("spcv_block",
  range = 1000, folds = 2,
  selection = "checkerboard")

autoplot(resampling_block_checkerboard,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-rows-and-cols, fig.cap='Random resampling of a specifid number of rectangular blocks as implemented in package blockCV (method "spcv\\_block" in mlr3spatiotempcv with arguments rows = 6 and cols = 3).', out.width="40%", fig.pos="ht"}
resampling_block_rows_cols = rsmp("spcv_block",
  rows = 6, cols = 3, folds = 5
)

autoplot(resampling_block_rows_cols,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r env-1, fig.cap='Environmental leave-one-block-out CV from package blockCV using a single predictor to define blocks in feature space (method "spcv\\_env" in mlr3spatiotempcv with argument features = "distdeforest").', out.width="40%", fig.pos="ht"}
resampling_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

autoplot(resampling_env,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

<!-- TODO: AB: should be combined with the previous figure into a two-panel figure. Differences are much easier to recognize if plotted next to each other. -->
```{r env-2, fig.cap='Environmental leave-one-block-out CV from package blockCV using two predictors to define blocks in feature space (method "spcv\\_env" in mlr3spatiotempcv with argument features = c("distdeforest", "slope")).', out.width="40%", fig.pos="ht"}
resampling_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)

autoplot(resampling_env_multi,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
<!-- AB: TODO: In general, the code would look much simpler if we could get rid of the scale_x/y_continuous() calls. Improve default settings of autoplot()? -->

@@

resampling_cstf_time = rsmp("sptcv_cstf", folds = 5, time_var = "Date")
resampling_cstf_time$instantiate(task_spt)

autoplot(resampling_cstf_time,
  fold_id = 5, task = task_spt, plot3D = TRUE
)
```

@@

```{r results='hide'}
resampling_cstf_loc = rsmp("sptcv_cstf", folds = 5, space_var = "SOURCEID")
resampling_cstf_loc$instantiate(task_spt)

autoplot(resampling_cstf_loc,
  fold_id = 5, task = task_spt, plot3D = TRUE)
```

@@

```{r results='hide'}
resampling_cstf_time_loc = rsmp("sptcv_cstf",
  folds = 5,
  space_var = "SOURCEID", time_var = "Date")
resampling_cstf_time_loc$instantiate(task_spt)

autoplot(resampling_cstf_time_loc,
  fold_id = 4, task = task_spt, plot3D = TRUE,
  show_omitted = TRUE)
```

@@

Next, the created resampling object `resampling_nsp` is passed to function `resample()` together with the task and learner objects created earlier to execute the model assessment.
This is the actual, potentially time-consuming CV estimation. With the present settings, eight random forest classifiers are fitted and evaluated in this step.

@@

```{r rr-nspcv, cache.lazy = FALSE}
resampling_nsp = rsmp("repeated_cv", folds = 4, repeats = 2)
resampling_nsp$instantiate(task)
rr_nsp = resample(
  task = task, learner = learner,
  resampling = resampling_nsp
)

rr_nsp$aggregate(measures = msr("classif.auc"))
```

@@

```{r rr-spcv, cache.lazy = FALSE}
resampling_sp = rsmp("repeated_spcv_coords", folds = 4, repeats = 2)
resampling_sp$instantiate(task)
rr_sp = resample(
  task = task, learner = learner,
  resampling = resampling_sp
)

rr_sp$aggregate(measures = msr("classif.auc"))
```

@@

```{r vis-spcv, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8}
autoplot(resampling_sp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

```{r vis-nspcv, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8}
autoplot(resampling_nsp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

>>>>

```{r buffer-non-eval, eval=FALSE}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
rsmp_buffer = rsmp("spcv_buffer", theRange = 1000)
rsmp_buffer$instantiate(task)

autoplot(rsmp_buffer, size = 0.8, task = task, fold_id = 1)
```

```{r buffer-eval, fig.cap='Visualization of the spatial buffering method from package blockCV (method "spcv\\_buffer" in  mlr3spatiotempcv). The buffer distance is 1000 m.', out.width="40%", fig.pos="ht",echo=FALSE}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
rsmp_buffer = rsmp("spcv_buffer", theRange = 1000)
rsmp_buffer$instantiate(task)

autoplot(rsmp_buffer,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

<!-- AB: TODO: folds = 5 makes very little sense in the case of LODO-CV, since this would only sample 5 discs, which cover only a small fraction of the study area. Let's use folds = 100, this will at least make readers think about their choice of #folds. -->

```{r disc-non-eval, eval=FALSE}
rsmp_disc = rsmp("spcv_disc", folds = 100, radius = 300L, buffer = 400L)
rsmp_disc$instantiate(task)

autoplot(rsmp_disc,
  size = 0.8, task = task, fold_id = 1)
```

```{r disc-eval, fig.cap='Visualization of one training set / test set combination generated with the leave-one-disc-out method from package sperrorest (method "spcv\\_disc" in mlr3spatiotempcv). The disc has a radius of 300 m and is surrounded by a 400-m buffer.', out.width="40%", echo=FALSE,fig.pos="hb"}
library("mlr3")
library("mlr3spatiotempcv")
task = tsk("ecuador")
rsmp_disc = rsmp("spcv_disc", folds = 100, radius = 300L, buffer = 400L)
rsmp_disc$instantiate(task)

autoplot(rsmp_disc,
  size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r coords-non-eval, eval=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)$instantiate(task)

autoplot(rsmp_coords, size = 0.8, fold_id = 1, task = task)
```

```{r coords-eval, fig.cap='Leave-one-block-out CV based on $k$-means clustering of the coordinates as implemented in package sperrorest (method "spcv\\_coords" in mlr3spatiotempcv).', out.width="40%", fig.pos="ht", echo=FALSE}
rsmp_coords = rsmp("spcv_coords", folds = 5)$instantiate(task)

autoplot(rsmp_coords,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r tile-non-eval, eval=FALSE}
rsmp_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

autoplot(rsmp_tiles, size = 0.8, fold_id = 1, task = task)
```

```{r tile, fig.cap='Leave-one-block-out resampling from package sperrorest (method "spcv\\_tiles" in package mlr3spatiotempcv with argument nsplit = c(3,4) indicating the number of rows and columns).', out.width="40%", fig.pos="ht", echo=FALSE}
rsmp_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

autoplot(rsmp_tiles,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

<!-- TODO: AB: This diagram is inconsistent with the other diagrams - should display training and test samples. -->
```{r custom-cv-non-eval, eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

rsmp_custom = rsmp("custom_cv")
rsmp_custom$instantiate(task, f = zclass)

autoplot(rsmp_custom, size = 0.8, task = task, fold_id = 1)
```

```{r custom-cv, fig.cap='Leave-one-level-out (custom) resampling from package mlr3 (method "custom\\_cv"). A factor variable is used to define the partitions. Each color represents one partition.', out.width="40%", fig.pos="ht", echo=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

rsmp_custom = rsmp("custom_cv")
rsmp_custom$instantiate(task, f = zclass)

autoplot(rsmp_custom, size = 0.8, task = task, fold_id = 1) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-random-non-eval, eval=FALSE}
rsmp_block_random = rsmp("spcv_block", range = 1000, folds = 5)

autoplot(rsmp_block_random, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE)
```

```{r block-random, fig.cap='Random resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "random" in mlr3spatiotempcv). The size of the squares is 1000 m, and four out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht", echo=FALSE}
rsmp_block_random = rsmp("spcv_block", range = 1000, folds = 5)

autoplot(rsmp_block_random,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-systematic-non-eval, eval=FALSE}
rsmp_block_systematic = rsmp("spcv_block",
  range = 1000, folds = 5,
  selection = "systematic"
)

autoplot(rsmp_block_systematic, size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE)
```

```{r block-systematic, fig.cap='Sytematic resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "systematic" in mlr3spatiotempcv). The size of the squares is 1000 m, and four out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht", echo=FALSE}
rsmp_block_systematic = rsmp("spcv_block",
  range = 1000, folds = 5,
  selection = "systematic"
)

autoplot(rsmp_block_systematic,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-checkerboard, fig.cap='Checkerboard resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "checkerboard" in mlr3spatiotempcv). The size of the squares is 1000 m, and eleven out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht!"}
rsmp_block_checkerboard = rsmp("spcv_block",
  range = 1000, folds = 2,
  selection = "checkerboard")

autoplot(rsmp_block_checkerboard,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r block-rows-and-cols, fig.cap='Random resampling of a specifid number of rectangular blocks as implemented in package blockCV (method "spcv\\_block" in mlr3spatiotempcv with arguments rows = 6 and cols = 3).', out.width="40%", fig.pos="ht"}
rsmp_block_rows_cols = rsmp("spcv_block",
  rows = 6, cols = 3, folds = 5
)

autoplot(rsmp_block_rows_cols,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

@@

```{r env-1-non-eval, eval=FALSE}
rsmp_env = rsmp("spcv_env", features = "distdeforest", folds = 5)

rsmp_env_multi = rsmp("spcv_env", features = c("distdeforest", "slope"), folds = 5)

plot_env_single = autoplot(rsmp_env, size = 0.8, fold_id = 1, task = task)

plot_env_multi = autoplot(rsmp_env_multi, size = 0.8, fold_id = 1, task = task)

library("patchwork")
plot_env_single + plot_env_multi
```

@@

<!-- TODO: AB: should be combined with the previous figure into a two-panel figure. Differences are much easier to recognize if plotted next to each other. -->
```{r env-1-eval, fig.cap='Environmental leave-one-block-out CV from package blockCV using one (left, "distdeforest") and two (right, "distdeforest" and "slope") predictors to define blocks in the feature space.', out.width="100%", fig.pos="ht", echo=FALSE}
rsmp_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

rsmp_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)

plot_env_single = autoplot(rsmp_env,
  size = 0.6, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02))

plot_env_multi = autoplot(rsmp_env_multi,
  size = 0.6, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.02)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.02))

library("patchwork")
plot_env_single + plot_env_multi + plot_layout(guides = 'collect')
```
<!-- AB: TODO: In general, the code would look much simpler if we could get rid of the scale_x/y_continuous() calls. Improve default settings of autoplot()? -->

@@

rsmp_cstf_time = rsmp("sptcv_cstf", folds = 5, time_var = "Date")
rsmp_cstf_time$instantiate(task_spt)

autoplot(rsmp_cstf_time,
  fold_id = 5, task = task_spt, plot3D = TRUE
)
```

@@

```{r results='hide'}
rsmp_cstf_loc = rsmp("sptcv_cstf", folds = 5, space_var = "SOURCEID")
rsmp_cstf_loc$instantiate(task_spt)

autoplot(rsmp_cstf_loc,
  fold_id = 5, task = task_spt, plot3D = TRUE)
```

@@

```{r results='hide'}
rsmp_cstf_time_loc = rsmp("sptcv_cstf",
  folds = 5,
  space_var = "SOURCEID", time_var = "Date")
rsmp_cstf_time_loc$instantiate(task_spt)

autoplot(rsmp_cstf_time_loc,
  fold_id = 4, task = task_spt, plot3D = TRUE,
  show_omitted = TRUE)
```

@@

Next, the created resampling object `rsmp_nsp` is passed to function `resample()` together with the task and learner objects created earlier to execute the model assessment.
This is the actual, potentially time-consuming CV estimation. With the present settings, eight random forest classifiers are fitted and evaluated in this step.

@@

```{r rr-nspcv-1, cache.lazy = FALSE, results='hide'}
rsmp_nsp = rsmp("repeated_cv", folds = 4, repeats = 2)
rsmp_nsp$instantiate(task)
rr_nsp = resample(
  task = task, learner = learner,
  resampling = rsmp_nsp
)
```

```{r rr-nspcv-2, cache.lazy = FALSE}
rr_nsp$aggregate(measures = msr("classif.auc"))
```

@@

```{r rr-spcv-1, cache.lazy = FALSE, results='hide'}
rsmp_sp = rsmp("repeated_spcv_coords", folds = 4, repeats = 2)
rsmp_sp$instantiate(task)
rr_sp = resample(
  task = task, learner = learner,
  resampling = rsmp_sp
)
```

```{r rr-spcv-2, cache.lazy = FALSE}
rr_sp$aggregate(measures = msr("classif.auc"))
```

@@

```{r vis-spcv-non-eval, eval=FALSE}
autoplot(rsmp_sp, task, fold_id = c(1:2), size = 0.8)
```

```{r vis-spcv-eval, fig.cap="Spatial leave-one-block-out partitioning using coordinate-based clustering to create roughly equally sized polygonal blocks. Due to space limitations only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_sp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

```{r vis-nspcv-non-eval, eval=FALSE}
autoplot(rsmp_nsp, task, fold_id = c(1:2), size = 0.8)
```

```{r vis-nspcv-eval, fig.cap="Random (non-spatial) four-fold CV partitioning. Only the first two folds of the first repetition are shown.", fig.pos="ht", fig.height=6, fig.width=8, echo=FALSE}
autoplot(rsmp_nsp, task, fold_id = c(1:2), size = 0.8) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
